Normalization by Evaluation for Sized Dependent Types

### 2017-02-28 nbe/icfp17.tex
[ ICFP 17 ] Quick reading of Sec 5

In this section, we show that NbE is sound for judgmental equality,
i.e., that same normal form implies definitional equality.  The proof
follows \citet{abelCoquandDybjer:lics07} and
\citet{fridlenderPagano:tlca13} and defines a Kripke logical relation
$\LR \Gamma t T f A$ between a well-typed term $\Gamma \der t : T$ and
a value $f \in A$.
However, in contrast to the cited works,
the logical relation defined in the following will also yield a weak
head normalization theorem.

>>>>

In this section, we show that NbE is sound for judgmental equality,
i.e., that \emph{same normal form} implies \emph{definitional equality}.  The proof
follows \citet{abelCoquandDybjer:lics07} and
\citet{fridlenderPagano:tlca13} and defines a Kripke logical relation
$\LR \Gamma t T f A$ between a well-typed term $\Gamma \der t : T$ and
a value $f \in A$.
\LONGVERSION{
However, in contrast to the cited works,
the logical relation defined in the following will also yield a weak
head normalization theorem.
} % END LONG VERSION
